Consistent Polyhedral Surrogates via Embedding

### 2021-04-18 notes/top-k.tex
Also adding top k updates but incomplete

>>>>

\section{Cutting down on search space}
Consider the loss $L^{top-k} : \U \times \Y \to \reals_+$ given in equation~\eqref{eq:top-k-surrogate}.
This surrogate is defined originally on $\U = \reals^n$, but since the loss is polyhedral, we know it has a finite set of minimizers.
If we can find a finite representative set, we can easily embed these reports via the identity and more easily study the property elicited by this surrogate, and how it compares to the top-$k$ property it was originally designed for.

We will start with $\U = \reals^n$, and slowly narrow down to a finite representative set for $L^{top-k}$.

\begin{proposition}
	$\U' := \{u \in \reals^n_+ \mid \|u\|_0 \leq k\}$ is representative for $L^{top-k}$.
\end{proposition}
\begin{proof}
	This is Lemma~\ref{lem:extra-elts-zero}.
\end{proof}

\begin{proposition}
	The set $\U'' := \U' \cap [0,k]^n$ is representative for $L^{top-k}$.
\end{proposition}
\begin{proof}
	Corollary of Lemma~\ref{lem:top-threshold}, as any of the $k$ largest elements cannot be more than $1$ greater than its preceding element.
\end{proof}

\begin{proposition}
	\jessie{Incorporate no more than 1 higher than mean}
\end{proposition}

Now we move from an infinite to finite set via the function $\phi$
\begin{align*}
\phi(u)_i &= 
\begin{cases}
0 & u_i < 1\\
1 & \\
c(u) & \\
\end{cases}~,~
\end{align*}
where $c(u) = \frac{|M(u)| + k - 1}{k - |H(u)|}$ with $M(u)$ is the number of elements $i$ of $u_i$ so that $\phi(u)_i = 1$, and $H(u)$ is the number of elements of $u_i$ so that $\phi(u)_i > 1$.

\begin{proposition}
	$\R = \phi(\U'')$ and is a finite representative set for $L^{top-k}$.
\end{proposition}
\begin{proof}

\end{proof}

\begin{proposition}
	$\R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}$ is representative for $L^{top-k}$.
\end{proposition}
\begin{proof}
	Since $\U''$ is representative, we simply have to show there is a function $\phi : \U'' \to \R$ so that $u \in \U''$ minimizes $L^{top-k}$ implies $\phi(u)$ minimizes $L^{top-k}$.
	In particular, take the sets $H(u) = \{i \mid u_i > 1\}$ and $M(u) = \{i \mid u_i \in (0,1]\}$.
	Observe that for $H(\U'')$ and $M(\U'')$ have finite domains, and for all $u \in \U''$, we have $H(u) \cap M(u) = \emptyset$ and are subsets of $[n]$ by construction, and their sums $|H(u)| + |M(u)| \leq k$ by the restriction of $\U''$ that $\|u\|_0 \leq k$.
	Moreover, we can write $\R = \phi(\U'') = \{\frac{|M(u)| + k -1}{k - |h(u)|} \mathbf{1}_{H(u)} + \mathbf{1}_{M(u)} : u \in \U''\}$.
	It is just left to show $\R$ is representative for $L^{top-k}$.

	Suppose $u \in \U''$ minimizes $L^{top-k}$; we want to show $\phi(u)$ also minimizes $L^{top-k}$.
	By virtue of $u \in \U''$, we know we can write the expected loss 
	\begin{align*}
	\inprod{p}{L^{top-k}(u)} &= 1 - \bar u + \inprod{p}{u + \frac 1 k \min(u,\ones)}\\
	&= 1 - \bar{\phi(u)} + \inprod{p}{u + \frac 1 k \min(\phi(u),\ones)}\\
	&\geq 1 - \bar{\phi(u)} + \inprod{p}{u + \frac 1 k \min(u,\ones)}\\
	\end{align*}
	Claims: $\bar u \leq \bar{\phi(u)}$
	$\min(u, \ones) = \min(\phi(u), \ones)$
	If $u$ minimizes $L(u;p)$, then $\inprod{p}{u} \geq \inprod{p}{\phi(u)}$.
\end{proof}
